Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-06-01 draft/paper1_jenny.tex
Edit summary

    By using deep imaging from the HSC survey we have shown that the stellar mass 
    density profiles of massive central galaxies depend systematically on the mass 
    of their host dark matter halos. 
    Here we discuss the physical origin, scientific implications, and potential 
    caveats of this result.

\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
            Build-Up of Outer Envelopes}
    \label{ssec:twophase}

    {\bf Do we need two different sections and two different radial profile figures?}

    Our results are consistent with the picture that massive central galaxies form via 
    a ``two-phase'' scenario. 
    According to this theory, the cores of massive galaxies were formed at $z{\sim} 2$ 
    during an intense period of in-situ star formation. 
    The outskirts of massive galaxies are then built up via a more gradual second 
    phase of evolution (the ``ex-situ'' phase) which is dominated by mass growth via 
    the accretion of satellite systems. 
    Non-dissipative minor mergers mostly deposit stars on the outskirts of the 
    centrals and do not have large impact on the central \mden{} profile 
    (e.g. \citealt{Oogi2013, Bedorf2013}). 
    Hence, according to this picture, the outer stellar envelopes of massive centrals 
    should correlate with the masses of their host halos, in qualitative agreement with
    our findings.

    State of the art hydrodynamic simulations suggest that massive dark matter halos 
    have central galaxies that have outer stellar envelopes with shallow slopes 
    (e.g. \citealt{Pillepich2014}). 
    This is consistent with the results in Fig \ref{fig:prof_1}.

@@

    {\bf Have we looked at delta M as a function of Mtot?  I think that would be useful 
    for comparison with the Oser papers, for instance. }

@@

        \item We show that the \mden{} profiles of massive galaxies are generally quite 
            smooth out to 10 kpc but that there is a large but continuous scatter in the 
            amount of light in their outskirts. 
            {\bf KEEP? We argue that ``cD'' galaxies simply represent the tail end of a 
            distribution but that they are not a distinct class of massive galaxies.}

        \item {\bf How do profiles depend on Mstar?}

>>>>

    With the help of deep HSC images, we trace the stellar mass distributions of 
    $0.3 < z < 0.5$ massive galaxies out to $>100$ kpc, and reveal the mass-dependent 
    nature of their stellar halos.
    Here we briefly discuss the physical origin, scientific implications, and potential 
    caveats of these results.

    % TODO: Move to Paper II
    %By using deep imaging from the HSC survey we have shown that the stellar mass 
    %density profiles of massive central galaxies depend systematically on the mass 
    %of their host dark matter halos.

%% ------------------------------------------------------------------------------------ %% 
\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
            Build-Up of Outer Envelopes}
    \label{ssec:twophase}

    The mass-dependent nature we find in the \mden{} and ellipticity profiles of 
    massive galaxies are consistent with the two-phase formation scenario. 
    According to this theory, the ``cores'' of massive central galaxies are formed 
    at $z{\sim} 2$ during an intense period of in-situ star formation. 
    The outskirts of massive galaxies are then built up through a more gradual second 
    phase of evolution (the ``ex-situ'' phase) that is dominated by mass assembly via 
    accretion and merger.
    Non-dissipative mergers, especially the minor ones, mostly deposit stars in the 
    outskirts of the centrals and do not have large impact on the central \mden{} 
    profile (e.g. \citealt{Oogi2013, Bedorf2013}).
    Given the stochastic nature of the merging process, it is easy to understand why 
    the \mden{} profiles of massive galaxies are similar in the inner region but show
    large and continuous scatter in the outskirt.

    State of the art hydrodynamic simulations of massive galaxy formation predict 
    that the fraction of accreted stars should strongly depend on their stellar mass 
    (e.g. \citealt{RodriguezGomez2016} \addref{}). 
    The increasingly more prominent stellar halos in more massive galaxies could 
    reflect this point, assuming the stars in the outskirts are dominated by accreted 
    ones.  
    The negative color gradients we see in these massive galaxies may support this 
    assumption. 
    The slightly bluer color in their outskirts are consistent with the picture that 
    the stars there are from less massive galaxies on the ``red-squence''.

    % Ellipticity of accreted stars.

    It would be interesting to make detailed comparison with these simulations to see
    if they can reproduce the observed

    % TODO: Move to paper II     
    %State of the art hydrodynamic simulations suggest that massive dark matter halos 
    %have central galaxies that have outer stellar envelopes with shallow slopes 
    %(e.g. \citealt{Pillepich2014}). 
    %This is consistent with the results in Fig \ref{fig:prof_1}.

    %Hence, according to this picture, the outer stellar envelopes of massive centrals 
    %should correlate with the masses of their host halos, in qualitative agreement with
    %our findings.

%% ------------------------------------------------------------------------------------ %% 
\subsection{Aperture Masses as Proxies of In-Situ and Accreted Stars}
    \label{ssec:insitu}

@@

    % TODO: Comparison with Illustris.

@@

        \item We show that the \mden{} profiles of massive galaxies within inner 
            10-20 kpc generally show similar slopes and have relative small scatter. 
            Meanwhile, there is a large but continuous scatter in the outskirts of 
            \mden{} profiles that suggests the stellar halos of these massive galaxies 
            are not self-similar. 
            Galaxies with higher \mtot{} show more prominent stellar halos and have 
            shallower outer \mden{} slopes than the less massive ones. 
            Assuming the stellar halos are dominated by accreted stars, the result is 
            in consistent with the two-phase formation picture of massive galaxies.

        \item We show that, on average, massive galaxies have positive ellipticity 
            gradient out to at least 60 kpc. 
            The average ellipticity profiles also depend on \mtot{}: more massive 
            galaxies tend to have steeper ellipticity gradients and become more 
            elongated in the accreted stellar halo. 
            On the other hand, the average $g-r$ and $g-i$ color gradients do not 
            show clear dependence on \mtot{} within 10-60 kpc.
